%! Author = marcus
%! Date = 04.11.24

\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{hyperref}

\geometry{margin=2.5cm}

\begin{document}

  \begin{titlepage}
    \begin{center}
      \vspace*{2cm}
      {\huge\bfseries ?Movie Finder?\par}
      \vspace{2cm}
      {\Large Group Number: 08\par}
      \vspace{1.5cm}
      {\large\bfseries Group Members:\par}
      \vspace{0.5cm}
      {\large
      Name 1 (Role)\par
      Name 2 (Role)\par
      Name 3 (Role)\par
      Name 4 (Role)\par
      }
      \vfill
      {\large \today\par}
    \end{center}
  \end{titlepage}

  \tableofcontents
  \newpage

  \section{Abstract}

  A platform aims to help users find movies they want to watch by curating a selection based on their preferences.
  The platform uses a transformer-based architecture to process user queries and rank movie recommendations based on similarity.
  The system adapts to user feedback, refining recommendations to provide the most relevant content.

  \section{Idea}

  In today’s world, the sheer volume of content available is overwhelming.
  It’s challenging for many to find movies they genuinely want to watch amidst a sea of irrelevant material.
  Streaming providers and online distributors possess the potential to curate a concise selection for their users.
  However, many of them choose not to do so.
  The reasons behind this decision remain unclear, but it’s possible that it’s a strategy to keep users locked into their platforms for as long as possible.
  Instead of offering users a curated selection, they’re presented with a flood of mediocre content that’s nowhere near what they’re truly interested in.
  Our mission is to value the time of users by making it easier for them to watch the movies they genuinely want to see.
  To achieve this, we’re building a platform where users can explicitly define their movie preferences, whether it’s general tastes or specific preferences for the moment.
  The system then diligently searches through a vast movie database to find an appropriate and concise selection that aligns with the user’s criteria.
  The top results are presented to the user with brief descriptions of the movie’s content, genre, actors, release date, and title.
  If the user isn’t satisfied with the provided content, the system adapts and re-searches the database using the modified criteria.
  Alternatively, if the user finds a movie they enjoy, we strive to minimize the barriers to starting a movie by directly recommending a few services that offer the selected content.
  With a single click, users can seamlessly switch to their favorite streaming platform, stream or purchase the movie, and enjoy it without any hassle.

  \subsection{Goal}
  Our mission is to value human time by simply recommending movies they genuinely want to watch, without forcing them to sift through a catalog of irrelevant content.
  The demand for such a service will only increase over time as the number of movies and series created continues to grow exponentially.
  In fact, there are now more TV shows produced in a given period than ever before, and this trend appears to persist.

  \section{Main Task}

  Our primary objective is to design an advanced information retrieval system for movie recommendations, employing a transformer-based architecture.
  To accomplish this, our core component will comprise a fusion of transformer models, including:
  \begin{itemize}
    \item to perform text encoding
    \item for text summarization
    \item as a sentence transformer for semantic similarity
  \end{itemize}

  \noindent Technically, the retrieval pipeline will work approximately as follows:
  \begin{itemize}
    \item Processing the user’s query, capturing their preferences.
    \item Document encoding of the movie preferences retrieved from the dataset.
    \item Calculating the similarity between the encoded user query and the encoded movie document.
    \item Ranking the results based on their relevance to the user.
  \end{itemize}

  \noindent After the initial phase of the retrieval pipeline concludes, the user has the option to assess their satisfaction with the results or to disregard irrelevant recommendations.
  If a selection of irrelevant content is made, the system will adapt and present a new selection based on the evolving user preferences.
  This approach aims to deliver the highest quality recommendations while minimizing the user’s effort.

  \section{Dataset and Processing}

  This section delves into the details of the sources and processing of used data.

  \subsection{Data Sources}

  Our movie database is sourced from the ``wykonos/movies'' dataset, which is loaded through Hugging Face.
  The dataset comprises various features, including id, title, genre, original language, overview, popularity, production companies, release date, budget/revenue, runtime, status, tagline, average vote, vote count, credits, and keywords.\newline\newline
  \noindent Additionally, we require a provider for captions/subtitles to generate informative summaries or recommendations based on the actual content of the movies.
  This provider will be contacted, and their data fetched through the backend of the system.
  This feature can be easily implemented using a simple REST-API. Currently, we are searching for a cost-effective or free option to fulfill this requirement. (TODO)

  \subsection{Data Processing}

  Before utilizing the dataset, we need to preprocess it through a data ``cleaning'' step.
  During this procedure, missing values (NaN) are replaced with empty strings to prevent future issues.
  Subsequently, each entry in the dataset is converted to strings.

  \section{Methods and Models}

  This section delves into the technical details of how our previously defined IR problem will be solved.

  \subsection{System Architecture}

  TODO

  \subsection{Implementation}

  The entire backend of the system will be implemented using Python.
  There are numerous useful libraries and tools that are beneficial for working on the given problem, such as PyTorch, Pandas, NumPy, and SciPy.
  The initial step is to perform the necessary input processing (encoding).
  For this purpose, an optimized transformer model will be utilized.
  Subsequently, we will use the model generated from the tokenized input to perform mean pooling of the last hidden states for similarity computation later on.
  In addition to the user input, we will also encode the movie descriptions.
  This enables us to compute a similarity measurement between the user input and the movie description (for instance, using cosine similarity).
  To provide the user with only the most relevant recommendations, a sophisticated ranking mechanism based on the similarity scores will be applied.
  Only the top three results, enriched with various additional movie metadata and a summary/recommendation of the content, will be displayed to the user.
  To generate the summary, we will first make a request to a caption/subtitle provider and then use the returned data in a summarization pipeline with an appropriate model.
  The recommendation will then be visualized in the frontend, which will be implemented using a modern web technology stack, including but not limited to NextJS.
  The recommendation can then be evaluated by the user, and in the case of dissatisfaction, it can be re-evaluated by the model to update the recommendation using a selection of irrelevant movies suggested by the user.

  \subsection{Optimization questions}
  Due to the size of the dataset, various optimization questions arise.
  These include topics such as memory management strategies, enhanced scalability through batch processing and hardware acceleration (CUDA/MPS).

  \section{Evaluation}
  \subsection{Metrics}

  \subsection{Results}

  \subsection{Discussion}


\end{document}
